---
title: "Marketing Spend and Customer Purchases"
author: "Jacqueline Gunawan"

format: html
editor: visual
execute:
  echo: false
  warning: false
  messages: false
  
bibliography: references.bib
---

```{r}
library(tidyverse)
library(readr)
library(knitr)
library(dslabs)
library(ggplot2)

Marketing_data <- read_csv("data/34666869_Jacqueline Gunawan.csv")
```

## Purpose

This report investigates the effectiveness of a personalized marketing campaign conducted over the past quarter. Specifically, it examines whether increasing marketing spend per customer leads to higher purchase amounts. Understanding this relationship is important for improving the efficiency of marketing budgets. The findings will help guide the allocation of marketing resources in the future.

## Research Question

The aim of this report is to determine whether or not a higher marketing spend per customer leads to increased purchase amounts or visits. The analysis focuses on identifying trends and relationships between these variables. The goal is to evaluate whether increased spending translates into meaningful revenue gains.

## Dataset

### Introduction

```{r}
cleaned_data <- Marketing_data |>
  mutate(
    notes = str_replace(notes, "N/A", "NA"),
    signup_date = as.Date(signup_date, tryFormats = c("%Y-%m-%d", "%Y/%m/%d"))
  ) |>
  filter(!is.na(purchase_amount)) |>
  select(-notes)
```

The dataset contains customer-level data from a personalized marketing campaign. It includes variables such as marketing spend per customer and purchase amount, along with other customer attributes. Prior to analysis, the dataset was cleaned by standardizing inconsistent date formats and handling missing variables in key variables such as purchase amount. Non-essential values, such as notes, were excluded from the analysis to improve clarity. The cleaned dataset is used to examine the relationship between marketing spend and customer purchases.

### Description

The dataset contains `r nrow(cleaned_data)` observations and `r ncol(cleaned_data)` variables. The dataset consists of a mix of numeric and categorical variables. Numeric variables include marketing spend, purchase amount, and number of visits, while the segment variable is categorical. @tbl-avg-keyfigures presents summary statistics of key variables, showing the average marketing spend, purchase amount, and number of visits across customers. @fig-marketing-distribution illustrates the distribution of marketing spend, indicating that spending varies across customers rather than being uniform. These summaries provide context for understanding how marketing efforts differ across the dataset before analyzing their impact on purchase behavior.

```{r}
#| label: tbl-avg-keyfigures
#| tbl-cap: "Summary statistics of key variables"

cleaned_data |>
  summarise(
    avg_spend = mean(marketing_spend),
    avg_purchase = mean(purchase_amount),
    avg_visits = mean(visits)
  ) |>
  kable()
```

```{r}
#| label: fig-marketing-distribution
#| fig-cap: "Distribution of Marketing Spend."

ggplot(cleaned_data, aes(x = marketing_spend)) +
  geom_histogram(bins = 20) +
  labs(
    title = "Distribution of Marketing Spend",
  )
```

## Results

```{r}
#| label: fig-spend-vs-purchase
#| fig-cap: "Relationship between marketing spend and purchase amount."

ggplot(cleaned_data, aes(x = marketing_spend, y = purchase_amount)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Marketing Spend vs Purchase Amount",
    x = "Marketing Spend",
    y = "Purchase Amount"
  )
```

@fig-spend-vs-purchase shows a positive relationship between marketing spend and purchase amount. As marketing spend increases, purchase amounts also tend to increase, although there is noticeable variation across customers. The fitted regression line highlights an overall upward trend, suggesting that higher marketing investment is generally associated with higher customer spending. This indicates that increasing marketing spend per customer may lead to higher purchase amounts, supporting the research question.
