---
title: "Marketing Spend and Customer Purchases"
author: "Jacqueline Gunawan"

format: html
editor: visual
execute:
  echo: false
  warning: false
  messages: false
---

```{r}
library(tidyverse)
library(readr)
library(knitr)
library(dslabs)
library(ggplot2)

Marketing_data <- read_csv("data/34666869_Jacqueline Gunawan.csv")
```

## Purpose

This report investigates the effectiveness of a personalized marketing campaign conducted over the past quarter. Specifically, it examines whether increasing marketing spend per customer leads to higher purchase amounts. Understanding this relationship is important for improving the efficiency of marketing budgets. The findings will help guide the allocation of marketing resources in the future.

## Research Question

The aim of this report is to determine whether or not a higher marketing spend per customer leads to increased purchase amounts or visits. The analysis focuses on identifying trends and relationships between these variables. The goal is to evaluate whether increased spending translates into meaningful revenue gains.

## Dataset

### Introduction

```{r}
cleaned_data <- Marketing_data |>
  mutate(
    notes = str_replace(notes, "N/A", "NA"),
    signup_date = as.Date(signup_date, tryFormats = c("%Y-%m-%d", "%Y/%m/%d"))
  ) |>
  filter(!is.na(purchase_amount)) |>
  select(-notes)
```

The dataset contains customer-level data from a personalized marketing campaign. It includes variables such as marketing spend per customer and purchase amount, along with other customer attributes. Prior to analysis, the dataset was cleaned by standardizing inconsistent date formats and handling missing variables in key variables such as purchase amount. Non-essential values, such as notes, were excluded from the analysis to improve clarity. The cleaned dataset is used to examine the relationship between marketing spend and customer purchases.

### Description

The dataset contains `r nrow(cleaned_data)` observations and `r ncol(cleaned_data)` variables. The dataset consists of a mix of numeric and categorical variables. Numeric variables include marketing spend, purchase amount, and number of visits, while the segment variable is categorical.

```{r}

```

## References

<https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/as.Date>
